---
title: "Hitzemonitor"
project: 
    type: website

format: 
    dashboard:
        expandable: false
        scrolling: false
        orientation: rows
        nav-buttons: 
            - icon: "envelope"
              href: "mailto:matthias.schnetzer@akwien.at"
            - icon: "github"
              href: "https://github.com/mschnetzer"
            - icon: "bluesky"
              href: "https://bsky.app/profile/matschnetzer.bsky.social"
theme: 
    - solar
    - heat_dash.scss

---

```{r setup}
#| include: false
#| echo: false
#| message: false
#| warning: false
librarian::shelf(tidyverse,lubridate, httr, jsonlite, glue, scales, bslib, bsicons, quarto, gghighlight, rvest, janitor, stringi, countrycode, htmlwidgets, shiny, MetBrewer, plotly, giscoR, DT, patchwork)
```

```{r data}
#| include: false
#| echo: false
#| message: false
#| warning: false

meta <- GET("https://dataset.api.hub.geosphere.at/v1/station/historical/klima-v2-1y/metadata")
metadat <- fromJSON(rawToChar(meta$content))
stations <- map_dfc(metadat$stations, ~ .x) |> 
  filter(is_active == TRUE & year(valid_to) >= year(today())) |> 
  mutate(n = n(), .by = name) |> 
  filter(n == 1 | type == "COMBINED") |> 
  select(id, name, state, lat, lon, altitude)

tempwien <- GET(glue::glue("https://dataset.api.hub.geosphere.at/v1/station/historical/klima-v2-1d?parameters=tlmax,tlmin,rr&start=1985-01-01&end={today()}&station_ids=5925"))

temphowa <- GET(glue::glue("https://dataset.api.hub.geosphere.at/v1/station/historical/klima-v2-1m?parameters=tlmax_mittel&start=1900-01-01&end={today()}&station_ids=105"))

tempaut <- GET(glue::glue("https://dataset.api.hub.geosphere.at/v1/station/historical/klima-v2-1y?parameters=tlmax,tage_tropen&start=1950-01-01&end={today()}&station_ids={paste0(stations$id, collapse = ',')}"))

tempaut_thisyear <- GET(glue::glue("https://dataset.api.hub.geosphere.at/v1/station/historical/klima-v2-1d?parameters=tlmax&start={year(today())}-01-01&end={today()}&station_ids={paste0(stations$id, collapse = ',')}"))

tempglobal <- GET("https://www.ncei.noaa.gov/access/monitoring/climate-at-a-glance/global/time-series/globe/tavg/land/12/12/1900-2026/data.json")

wiendata <- fromJSON(rawToChar(tempwien$content))
howadata <- fromJSON(rawToChar(temphowa$content))
autdata <- fromJSON(rawToChar(tempaut$content))
autdata_thisyear <- fromJSON(rawToChar(tempaut_thisyear$content))
globaldata <- fromJSON(rawToChar(tempglobal$content))

atmap <- gisco_get_nuts(year = 2024, country = "AT", nuts_level = "2", resolution = "3", epsg = 4326)

# Daily data for Vienna
wien <- tibble(
  tlmax = wiendata$features$properties$parameters$tlmax$data,
  tlmin = wiendata$features$properties$parameters$tlmin$data,
  rr = wiendata$features$properties$parameters$rr$data) |>
  mutate(timestamp = list(wiendata$timestamps)) |>
  unnest(c(tlmax, tlmin, rr, timestamp)) |> 
  mutate(timestamp = as.Date(timestamp))

# Long time series for Hohe Warte
howa <- tibble(
  tlmax = howadata$features$properties$parameters$tlmax$data) |>
  mutate(timestamp = list(howadata$timestamps)) |>
  unnest(c(tlmax, timestamp)) |> 
  mutate(timestamp = as.Date(timestamp))

# Annual data for Austria except current year
autmax_hist <- tibble(station = autdata$features$properties$station,
  tlmax = autdata$features$properties$parameters$tlmax$data,
  tage_tropen = autdata$features$properties$parameters$tage_tropen$data) |>
  mutate(timestamp = list(autdata$timestamps)) |>
  unnest(c(tlmax, tage_tropen, timestamp)) |> 
  mutate(time = year(timestamp)) |>
  left_join(stations, by = c("station" = "id")) 

# Current year for Austria
autmax_current <- tibble(station = autdata_thisyear$features$properties$station,
  tlmax = autdata_thisyear$features$properties$parameters$tlmax$data) |>
  mutate(timestamp = list(autdata_thisyear$timestamps)) |>
  unnest(c(tlmax, timestamp)) |> 
  filter(!is.na(tlmax)) |>
  mutate(timestamp = as.Date(timestamp), hitzetag = ifelse(tlmax >= 30, 1, 0), time = year(timestamp)) |>
  reframe(tlmax = max(tlmax, na.rm = TRUE), tage_tropen = sum(hitzetag, na.rm = TRUE), .by = c(station, time)) |>
  left_join(stations, by = c("station" = "id")) 

# Global temperature departure from long-term mean (1901-2000)
globaldev <- tibble(
  year = as.integer(names(globaldata$data)),
  departure = map_dbl(globaldata$data, ~ .x$departure))

# Combined Austria data
austria <- autmax_hist |> select(-timestamp) |> 
  bind_rows(autmax_current) 

url <- "https://en.wikipedia.org/wiki/List_of_weather_records#Highest_temperatures_ever_recorded"
raw <- data.frame()
records <- url |> 
  read_html() |> 
  html_nodes(xpath = '//*[@id="mw1A"]') |> 
  html_table(fill=TRUE) |> 
  nth(1)

rekorde <- records |> clean_names() |> 
  mutate(country = stri_extract_first_regex(country_region, "^[^\\(]+"),
         year = as.numeric(stri_extract_last_regex(date, "\\d{4}")),
         temp = as.numeric(stri_extract_first_regex(temperature, "[:graph:]+(?= ?)")),
         continent = fct_rev(ifelse(is.na(temp), country_region, NA))) |> 
  fill(continent) |>
  select(country,year,temp,continent, date) |> 
  mutate(continent = fct_recode(continent, "Afrika" = "Africa", "Antarktis" = "Antarctica", "Asien" = "Asia",
                              "Europa" = "Europe", "Nordamerika" = "North America", 
                              "Ozeanien" = "Oceania", "Südamerika" = "South America"),
        ccode = countrycode(country, origin = "country.name", destination = "iso3c")) |>
  drop_na() |> 
  filter(continent != "Antarktis")

```

# Wien

## Row

```{r hitzetage}
tmax_filter <- wien |> 
  filter(month(timestamp) < month(today()) |
    (month(timestamp) == month(today()) & day(timestamp) <= day(today()))
  )

findat <- tmax_filter |>
  filter(tlmax >= 30) |>  count(year(timestamp), .drop = FALSE) |> 
  rename(year = `year(timestamp)`)

lasttmax <- findat |> slice_max(year, n = 1) |> pull(n)
avgtmax <- findat |> filter(year >= 1960, year <= 1990) |> summarise(avg = mean(n, na.rm = TRUE)) |> pull(avg)

value_box(
  theme = value_box_theme(bg = "#8e0808"),
  showcase = bsicons::bs_icon("sun"),
  title = "Hitzetage in Wien",
  value = scales::comma(lasttmax),
  p(glue::glue("{comma(lasttmax - avgtmax, accuracy = 1)} Tage {ifelse(lasttmax > avgtmax, 'mehr', 'weniger')} als Ø 1960-1990"))
)
```

```{r tropennächte}
tmin_filter <- wien |> 
  filter(month(timestamp) < month(today()) |
    (month(timestamp) == month(today()) & day(timestamp) <= day(today()))
  )

findat <- tmin_filter |>
  filter(tlmin >= 20) |>  count(year(timestamp), .drop = FALSE) |> 
  rename(year = `year(timestamp)`)

lasttmin <- findat |> slice_max(year, n = 1) |> pull(n)
avgtmin <- findat |> filter(year >= 1960, year <= 1990) |> summarise(avg = mean(n, na.rm = TRUE)) |> pull(avg)

value_box(
  theme = value_box_theme(bg = "#ba3f01"),
  showcase = bsicons::bs_icon("moon-stars"),
  title = "Tropennächte in Wien",
  value = scales::comma(lasttmin),
  p(glue::glue("{comma(lasttmin - avgtmin, accuracy = 1)} Nächte {ifelse(lasttmin > avgtmin, 'mehr', 'weniger')} als Ø 1960-1990"))
)
```

```{r atrekord}
wienrekord <- austria |>
  filter(state == "Wien") |>
  slice_max(tlmax, n = 1)

value_box(
  theme = value_box_theme(bg = "#c57300"),
  showcase = bsicons::bs_icon("thermometer-sun"),
  title = "Hitzerekord in Wien",
  value = scales::comma(wienrekord$tlmax, suffix = "°C", accuracy = .1),
  p(glue::glue("gemessen {wienrekord$time} in {wienrekord$name}"))
)
```

## Row {.fill}

### Column {width=55%}

::: {.card title="Temperaturabweichung vom langfristigen Mittel (1900-2000)<i class='bi bi-hourglass-split'></i>" .fill}

```{r abweichungen}
reference_means <- howa |> 
  filter(year(timestamp) %in% 1900:2000) |> 
  mutate(monthname = month(timestamp, label = T, abbr = T, locale = "de_DE.UTF-8")) |> 
  summarise(ref_tlmax = mean(tlmax, na.rm = TRUE), .by = monthname)

month_means <- howa |> 
  mutate(monthname = month(timestamp, label = T, abbr = T, locale = "de_DE.UTF-8"),
          yr = year(timestamp)) |> 
  left_join(reference_means, by = "monthname") |> 
  mutate(abw = tlmax - ref_tlmax) |> 
  mutate(ihs = log(abw + sqrt(abw^2+1)))
  
abw <- month_means |> 
  filter(year(timestamp) >= 1970) |> 
  ggplot(aes(x = yr,  y = monthname, fill = ihs, text = glue::glue("{monthname} {yr}: {label_number(style_positive = 'plus', accuracy = 0.1)(abw)}°C"))) +
  geom_tile(color = "white", size = 0.25) +
  scale_x_continuous(position = "top", expand = c(0.005,0)) +
  scale_y_discrete(limits = rev) +
  scale_fill_gradient2(low = "darkblue", mid = "grey98", high = "darkred") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Roboto Condensed", base_size = 14) + 
  theme(panel.grid = element_blank(),
        plot.background = element_rect(fill= "transparent", color = NA),
        panel.background = element_rect(fill= "transparent", color = NA),
        legend.position = "none",
        axis.text.y = element_text(),
        axis.text = element_text(color = "white"))

ggplotly(abw, tooltip = "text") |>
    layout(hovermode = "closest", hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed", size = 16)),
            xaxis=list(side="top")) |> 
    config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)
```

:::

### Column {width=45%}

#### Row {.fill}

::: {.card title="Extremwetterereignisse in Wien<i class='bi bi-graph-up'></i>" .fill}

<div class="btn-group heat-toggle" role="group">
  <button id="show-hot" class="btn btn-hot active" type="button">
    Hitzetage (≥30°C)
  </button>
  <button id="show-night" class="btn btn-night" type="button">
    Tropennächte (≥20°C)
  </button>
  <button id="show-rain" class="btn btn-rain" type="button">
    Starkregentage (≥25l/m²)
  </button>
</div>

```{r extremverlauf}
data <- fromJSON(rawToChar(tempwien$content))

tmax <- map_dfc(data$features$properties$parameters$tlmax$data, ~ .x) |> 
  mutate(time = as.Date(data$timestamps)) |> 
  rename(tmax = `...1`) |> 
  filter(tmax >= 30) |> 
  count(year(time), .drop = FALSE) |> 
  rename(year = `year(time)`, Hitzetage = n)

tmin <- map_dfc(data$features$properties$parameters$tlmin$data, ~ .x) |> 
  mutate(time = as.Date(data$timestamps)) |> 
  rename(tmin = `...1`) |> 
  filter(tmin >= 20) |> 
  count(year(time), .drop = FALSE) |> 
  rename(year = `year(time)`, Tropennächte = n)

nied <- map_dfc(data$features$properties$parameters$rr$data, ~ .x) |> 
  mutate(time = as.Date(data$timestamps)) |> 
  rename(nied = `...1`) |> 
  filter(nied >= 25) |> 
  count(year(time), .drop = FALSE) |> 
  rename(year = `year(time)`, Starkregentage = n)

tage <- tmax |>
  left_join(tmin, by = "year") |>
  left_join(nied, by = "year") |>
  pivot_longer(cols = c(Hitzetage, Tropennächte, Starkregentage), names_to = "type", values_to = "n") |> 
  mutate(type = factor(type, levels = c("Hitzetage", "Tropennächte", "Starkregentage")))


verlauf <- ggplot(tage, aes(x = year, y = n, fill = type, text = glue::glue("{year}: {n}"))) +
  geom_col(position = "identity") +
  scale_fill_manual(values = c("Hitzetage" = "#8e0808", "Tropennächte" = "#ba3f01", "Starkregentage" = "#007bff")) +
  scale_x_continuous(breaks = seq(1950, 2020, 10), expand = expansion(mult = c(0.02, 0.02))) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.02))) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(plot.background = element_rect(fill = "transparent", color = NA),
    panel.background = element_rect(fill = "transparent", color = NA),
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major = element_line(linewidth = 0.3, color = alpha("white", 0.3)),
    axis.text = element_text(color = "white"))

p <- ggplotly(verlauf, tooltip = "text")
p$elementId <- "heatplot"
p$x$data[[1]]$visible <- TRUE
p$x$data[[2]]$visible <- FALSE
p$x$data[[3]]$visible <- FALSE

p <- p |> 
  layout(hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed", color = "black", size = 16))) |>
  config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)

p

```

<script>
window.addEventListener("load", function () {
  const plot = document.getElementById("heatplot");
  const hot = document.getElementById("show-hot");
  const night = document.getElementById("show-night");
  const rain = document.getElementById("show-rain");
  hot.addEventListener("click", function () {
      Plotly.restyle(
          plot,
          {visible: [true,false,false]}
      );
      hot.classList.add("active");
      night.classList.remove("active");
      rain.classList.remove("active");
  });

  night.addEventListener("click", function () {
      Plotly.restyle(
          plot,
          {visible: [false,true,false]}
      );
      night.classList.add("active");
      hot.classList.remove("active");
      rain.classList.remove("active");
  });

  rain.addEventListener("click", function () {
      Plotly.restyle(
          plot,
          {visible: [false,false,true]}
      );
      rain.classList.add("active");
      hot.classList.remove("active");
      night.classList.remove("active");
  });
});
</script>

:::

#### Row

::: {.card title="Information<i class='bi bi-info-circle-fill'></i>" class="info-card" .flow}
Quellen: Geosphere, NOAAGlobalTemp, Wikipedia. Werte für Wien von Station Innere Stadt, außer Langfristtrend von Hohe Warte. Stand: `r format(today(), '%d.%m.%Y')`.
:::

# Österreich


## Row

```{r at_hitzetage}
at_hitzetage <- austria |> 
  filter(time == 2026) |> 
  slice_max(tage_tropen, n = 1, with_ties = FALSE)

value_box(
  theme = value_box_theme(bg = "#8e0808"),
  showcase = bsicons::bs_icon("sun"),
  title = glue::glue("Die meisten Hitzetage {at_hitzetage$time}"),
  value = scales::comma(at_hitzetage$tage_tropen),
  p(glue::glue("gemessen in {at_hitzetage$name}"))
)
```

```{r at_tagerekord}
at_tagerekord <- austria |> 
  slice_max(tage_tropen, n = 1, with_ties = FALSE)

value_box(
  theme = value_box_theme(bg = "#ba3f01"),
  showcase = bsicons::bs_icon("thermometer-sun"),
  title = "Rekord an Hitzetagen",
  value = scales::comma(at_tagerekord$tage_tropen),
  p(glue::glue("gemessen {at_tagerekord$time} in {at_tagerekord$name}"))
)
```

```{r at_rekord}
at_rekord <- austria |> 
  slice_max(tlmax, n = 1, with_ties = FALSE)

value_box(
  theme = value_box_theme(bg = "#c57300"),
  showcase = bsicons::bs_icon("fire"),
  title = "Die heißeste Temperatur",
  value = scales::comma(at_rekord$tlmax, suffix = "°C", accuracy = .1),
  p(glue::glue("gemessen {at_rekord$time} in {at_rekord$name}"))
)
```

## Row {.fill}

### Column {width=55%}

::: {.card title="Anzahl der Hitzetage in diesem Jahr<i class='bi bi-sun-fill'></i>" .fill}

```{r atmap}
heatmap <- atmap |> 
  ggplot() + 
  geom_sf(fill = "gray95") +
  geom_point(data = austria |> filter(!is.na(tage_tropen)) |> slice_max(time, n = 1, by = name), 
      aes(x = lon, y = lat, color = tage_tropen, text = glue::glue("<span style='color:darkred;font-size:120%;font-family:Roboto Condensed;'>{name}</span><br><span style='font-size:100%;font-family:Roboto Condensed;'>Höhe: {label_number(accuracy = 1, big.mark = '.')(altitude)}m</span><br><span style='font-size:100%;font-family:Roboto Condensed;'>{time}: {tage_tropen} Hitzetage</span>")), size = 2) +
  scale_color_gradient(low = "yellow", high = "darkred") +
  labs(x = NULL, y = NULL, color = "Hitzetage", size = "Hitzetage") +
  coord_sf(expand = FALSE) +
  theme_minimal(base_family = "Roboto Condensed", base_size = 14) +
  theme(legend.position = "none",
        plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())

ggplotly(heatmap, tooltip = "text") |>
    layout(hovermode = "compare", hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed"))) |> 
    config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)
```

:::

### Column {.fill}

::: {.card title="Jahreshöchstwerte seit 1950<i class='bi bi-thermometer-high'></i>" .fill}

```{r heattab}
austria |> drop_na() |> 
  select(time, name, state, tlmax) |> 
  slice_max(tlmax, by = time) |>
  distinct() |> 
  arrange(desc(tlmax)) |> 
  DT::datatable(colnames = c("Jahr", "Station", "Bundesland", "Höchsttemperatur"), class = "display", rownames = FALSE,
  options = list(info = F, paging = F, searching = F)) |> 
  formatStyle(columns = 1:4, fontSize = '80%')
```

:::

# International

## Row

### Column {width=65%}

#### Row {.fill}

::: {.card title="Globale Temperaturabweichung vom langjährigen Schnitt (1901-2000)<i class='bi bi-graph-up'></i>" .fill}
```{r globaldev}
globalplot <- globaldev |> 
  ggplot(aes(x = year, y = departure, fill = departure > 0, text = glue::glue("{year}: {label_number(accuracy = 0.01, style_positive = 'plus')(departure)}°C"))) +
  geom_col() +
  scale_fill_manual(values = c(`TRUE` = "darkred", `FALSE` = "darkblue"), guide = "none") +
  scale_x_continuous(breaks = seq(1900,2020,20  ), expand = expansion(mult = c(0.02, 0.02))) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.02))) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Roboto Condensed", base_size = 14) +
  theme(plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linewidth = 0.3, color = alpha("white", 0.3)),
        axis.text = element_text(color = "white", size = 10)) 

ggplotly(globalplot, tooltip = "text") |>
    layout(hovermode = "compare", hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed"))) |> 
    config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)
```
:::

#### Row {.fill}

::: {.card title="Neue Höchstwerte im Zeitverlauf<i class='bi bi-globe-europe-africa'></i>" .fill}

```{r int_timeline}
# timeline <- rekorde |> 
#   reframe(count = n(), countries = paste(glue::glue("{ccode} ({temp}°)"), collapse = "<br>"), .by = c(year, continent)) |> 
#   ggplot(aes(y = continent, x = year, color = continent, text = glue::glue("{year}<br>{countries}"))) +
#   geom_point(alpha = 0.8, aes(size = count)) +
#   geom_hline(aes(yintercept = continent, color = continent), linewidth = 0.6) +
#   scale_x_continuous(breaks = seq(1900,2020,20), expand = expansion(mult = c(0.05, 0.02))) +
#   scale_color_manual(values = met.brewer("Lakota"), name = NULL) +
#   scale_size_area(max_size = 7) +
#   labs(y = NULL, x = NULL) +
#   theme_minimal(base_family = "Roboto Condensed", base_size = 14) +
#   theme(legend.position = "none",
#         plot.background = element_rect(fill = "transparent", color = NA),
#         panel.background = element_rect(fill = "transparent", color = NA),
#         panel.grid.minor = element_blank(),
#         panel.grid.major = element_line(linewidth = 0.3, color = alpha("white", 0.3)),
#         axis.text = element_text(color = "white", size = 13))


# time_rec <- ggplotly(timeline, tooltip = "text") |>
#     layout(hovermode = "compare", hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed"))) |> 
#     style(showlegend = FALSE) |>
#     config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)

rekplot <- rekorde |> 
  reframe(count = n(), countries = paste(glue::glue("{ccode} ({temp}°)"), collapse = "<br>"), .by = c(year, continent)) |>
  ggplot(aes(x = year, y = count, fill=continent, 
              text = glue::glue("{year}<br>{continent}: {count} Rekord{ifelse(count > 1, 'e', '')}<br>{countries}"))) +
  geom_bar(stat = "identity", position = "stack") +
  scale_x_continuous(breaks = seq(1900,2020,20), expand = expansion(mult = c(0.02, 0.02))) +
  scale_fill_manual(values = met.brewer("Lakota"), name = NULL) +
  labs(y = NULL, x = NULL) +
  theme_minimal(base_family = "Roboto Condensed", base_size = 14) +
  theme(legend.text = element_text(color = "white", size = 12,
                  margin = margin(l = 0)),
        plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linewidth = 0.3, color = alpha("white", 0.3)),
        axis.text = element_text(color = "white", size = 10))

bar_rec <- ggplotly(rekplot, tooltip = "text") |>
    layout(hovermode = "compare",
    hoverlabel = list(bgcolor = "white", font = list(family = "Roboto Condensed")),
    legend = list(x = 0.05, y = 0.98, xanchor = "left", yanchor = "top",
                  orientation = "h", traceorder = "reversed", itemclick = FALSE, bgcolor = "rgba(0,0,0,0)")) |> 
    config(displayModeBar = FALSE, displaylogo = FALSE, responsive = TRUE)

# sum_stack_max <- rekplot$data |> summarise(total = sum(count), .by = year) |> pull(total) |> max()

# subplot(time_rec, bar_rec, nrows = 2, shareX = TRUE) |> 
#   layout(yaxis2 = list(autorange = FALSE, rangemode = "tozero"))

bar_rec
```

:::

### Column {.fill}

::: {.card title="Internationale Höchstwerte<i class='bi bi-globe'></i>" .fill}

```{r int_table}
rekorde <- rekorde |> 
  mutate(country.de = countrycode(ccode, origin = "iso3c", destination = "country.name.de"))

rekorde |>  
  select(temp, year, country.de, continent) |>
  arrange(desc(temp)) |>
  DT::datatable(colnames = c("Maximum", "Jahr", "Land", "Kontinent"), class = "display", rownames = FALSE,
  options = list(info = F, paging = F, searching = F)) |> 
  formatStyle(columns = 1:4, fontSize = '80%') |> 
  formatCurrency(columns = 1, currency = " °C", before = F, interval = 3, dec.mark = ",", digits = 1)
```

:::